\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage{ragged2e}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Saejin}{Mahlau-Heinert}
\address{221 W. Bayview Blvd}{Norfolk, VA, 23503}
\phone[mobile]{(757) 777-4868}
\email{saejinmh@gmail.com}


\begin{document}
\recipient{Daniel H. Wagner Associates, Inc}{Human Resources Administrator}
\date{April 1, 2017}
\opening{Dear Ms.\hspace{0.62mm}Teresa Lewis,}
\closing{Sincerely,}
\makelettertitle

\justify
I am a rising junior Computer Science major at Allegheny College, and am very excited to be applying for a summer internship at Daniel H. Wagner Associates. I learned about the position from a classmate who is in touch with an alumna currently employed at Wagner Associates.

Through my coursework and personal projects, I have developed strong interests in artificial intelligence (especially in neural and Bayesian networks), mathematics, and software development. Thus, I was immediately interested in this position as Wagner Associates' research and work in these areas would excellently complement my own studies and passions. In addition, I grew up among U.S. Navy personnel, and would greatly appreciate the opportunity to contribute my skills to research and development for the uniformed services.

Please do not hesitate to contact me for any additional materials or clarification. I am available through my email (saejinmh@gmail.com) or phone (757-777-4868). Thank you for your kind consideration.
\newline\newline


\makeletterclosing
\end{document}
